### 2018-04-29 paper/global-overlay-design.tex
yaaaay, outline figure

\subsection{The Global overlay}

@@

Every time a device is online, it participates in the random peer sampling 
protocol.
If a device is sampled it provides the following information:
\begin{itemize}
  \item its address, \(d\);
  \item its public key, \(\pk_d\);
  \item the probability of being online, \(p_d\).
\end{itemize}
We will denote this by the following algorithm \((d, \pk_d, p_d)\gets 
  \GetRandomPeer\), which will be used below.
The probability of being online, \(p_d\), is inferred as above 
(\cref{local-swarm}).

>>>>

\subsection{The Global Overlay}
\label{sec:global_overlay}

@@

Every time a device is online, it participates in the random peer sampling 
protocol.
If a device is sampled it provides the following information:
\begin{itemize}
  \item its address, $@_d$;
  \item its public key, \(\pk_d\);
  \item the probability of being online, $p_d=P\left[d \in O_{t+1} | S_t\right] $.
\end{itemize}
We will denote this by the following algorithm $(@_d, \pk_d, p_d)\gets 
  \GetRandomPeer$, which will be used below.
The probability of being online, \(p_d\), is inferred as above 
(\ref{sub:a_model_of_the_user_s_behavior}).

### 2018-04-29 paper/related.tex

\commentAL{Will need another pass.}
\paragraph*{Modeling devices' connection and disconnection} 
% To simulate users' devices participating in a distributed protocol, we build upon existing literature on two topics: 
% multi-device interaction, and churn in P2P networks. 
In our experiments, we simulate users' devices participating in a distributed protocol.
To make this simulation realistic, we based our models on existing literature.

>>>>

Cloud services for availability of files on multiple devices and sharing with others, such as Dropbox, Box, or iCloud, require trust in the service provider, at minimum to keep the service running without changes to the terms of service becoming unacceptable. Alternatively, users could set up their own cloud using a dedicated server or edge devices such as home gateways. This would require devices that users are less likely to already have than laptops or smartphones. P2P file sharing has been researched extensively, with respect to aspects such as architecture (starting with the semi-centralized Napster~\cite{napster}), availability and replication~\cite{gnutella, krz}, scalability~\cite{bittorrent}, anonymity~\cite{freenet, Tor}, and distributed hash tables (DHT)~\cite{opendht, can, chord, pastry}. In contrast to our work, the main goal was to enable dissemination to many users who do not necessarily know each other in person. Here, we focus on sharing files in a more deliberate yet ad-hoc manner, i.e., between users that out-of-band agree to share a file but do not keep it available for anyone else in the future. TOR~\cite{Tor}, although not designed for file sharing specifically, comes closest in that respect, but does not address the following aspect.

There is a concern shared with traditional p2p file sharing, namely churn and its effect on availability - here in the narrow context of the set of user devices based on user behavior. We thus discuss the related work on predicting user behavior next.

\commentAL{Will need another pass.}
\paragraph*{Modeling devices' connection and disconnection} 
% To simulate users' devices participating in a distributed protocol, we build upon existing literature on two topics: 
% multi-device interaction, and churn in P2P networks.

In our experiments, we simulate users' devices participating in a distributed protocol.
To make this simulation realistic, we based our models on existing literature.

### 2018-04-29 paper/squad-overlay-design.tex

We show in section~\ref{sub:devices_predictions_of_the_user_behavior} that $P\left[ d \in O_{t+1} \mid S_{t} = s \right] \simeq P\left[ d \in O_{t+i} \mid S_{t} = s \right]$. 
For that reason, devices only compute the prediction of their connection at $t+1$, that is considered a good enough estimator of their state ``in the near future''.

@@

>>>>

We show in section~\ref{sub:devices_predictions_of_the_user_behavior} that $P\left[ d \in O_{t+1} \mid S_{t} = s \right] \simeq P\left[ d \in O_{t+i} \mid S_{t} = s \right]$. 
For that reason, devices only compute the prediction of their connection at $t+1$, that is considered a good enough estimator of their connection state ``in the near future''.

@@

Given an initial estimate $\lambda_{N}^{(0)}$ of the model, and the sequence of observations $O$, the Baum-Welch algorithm uses Expectation-Maximization to iteratively compute the most likely $S^{(i)}$ and $\lambda_{N}^{(i)}$ until the probability of the observations using the estimated model falls below a predefined threshold: $P[O; \lambda_{N}^{(i)}] < \epsilon$.
Devices use this algorithm to infer their user's behavioral model from the observations.

It needs an initial model, though, with a predefined number of states $N$. 
$N$ is given by the user, and we set $\lambda_{N}^{(0)}$ to be a uniform model: probabilities of switching to each location are uniform, and all devices have a probability of being online of 0.5.

Baum-Welch usually requires a lot of data to fit the model $\lambda_N$ that generated $O$.
Indeed, $P[O; \lambda_{N}^{(i)}] < \epsilon$ does not mean that $\lambda_N \simeq \lambda_N^{(i)}$.
In our case, we do not care as long as the predictions using the estimated model, $P[O_{t+1} \mid S_t; \lambda_N^{(i)}]$, are close to the ground-truth, $P[O_{t+1} \mid S_t; \lambda_N]$.
This will be evaluated in section~\ref{sub:devices_predictions_of_the_user_behavior}.
